Add Plant Functional Type (PFT) labels

### 2021-03-29 R/add_plant_functional_type.Rmd
31 done

## R packages

@@

unique(cleaned_spectra$scientificName)

>>>>

  else if(genusSpecies == "Ailanthus altissima"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "tree of heaven"}

  else if(genusSpecies == "Prunus serotina"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "black cherrt"}

  else if(genusSpecies == "Celtis occidentalis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "common hackberry"}

  else if(genusSpecies == "Quercus alba"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "white oak"}

  else if(genusSpecies == "Juglans nigra"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "black walnut"}

  else if(genusSpecies == "Robinia pseudoacacia"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "black locust"}

  else if(genusSpecies == "Pinus strobus"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "eastern white pine"}

  else if(genusSpecies == "Carya glabra"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "pignut hickory"}

  else if(genusSpecies == "Tetradium daniellii"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "bee-bee tree"}

  else if(genusSpecies == "Juniperus virginiana"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "red cedar"}

  else if(genusSpecies == "Picea mariana"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "black spruce"}

## R packages: attempting to automate PFT labeling

@@
